Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-24 submission5/core.tex
Remove "capped"

\begin{figure*}
  \begin{subfigure}{0.4\textwidth}
    \[\mathit{range} ~ \reg ~ \mathit{off} ~ \mathit{sz} ~ \mach \triangleq
    \{\mach[\reg]+i | \mathit{off} \leq i < \mathit{off+sz}\}\]

    \judgmentbr{\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap \unsealed(V)\)}
               {\(V' = V \llbracket \addr \mapsto \object \mid \addr \in \components \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{f} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

@@

This essentially generalizes the above notion of passing: we will consider
a caller to have intentionally passed an object if that object is reachable by
a capability that has been passed to the callee. Reachability includes capabilities passed
indirectly, by being stored in an object that is in turn passed. We call
the set of reachable addresses \(\mathit{capped}\). The call operation in this setting
will seal only objects that are neither in \(\mathit{capped}\) nor the previously defined \(\mathit{passed}\).

>>>>

\begin{figure*}
  \begin{subfigure}{0.4\textwidth}
    \judgmentbr{\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap \unsealed(V)\)}
               {\(V' = V \llbracket \addr \mapsto \object \mid \addr \in \components \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{f} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

@@

This essentially generalizes the above notion of passing: we will consider
a caller to have intentionally passed an object if that object is reachable by
a capability that has been passed to the callee. Reachability includes capabilities passed
indirectly, by being stored in an object that is in turn passed. We define
the set of reachable addresses using \(\mathit{reach*}\), the transitive closure of elements
that can be reached from the arguments of the call. The call operation in this setting
will seal only objects that are not in \(\mathit{reach*}\) nor the previously defined \(\mathit{passed}\).
